---
title: "ps4_trf2122"
author: "Taylor Francisco"
date: "2023-12-08"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
rm(list=ls())
```

#Load Packages 
```{r}
library(quanteda)
library(tidyverse)
library(topicmodels)
library(quanteda.textstats)
library(quanteda.textmodels)
library(quanteda.textplots)
```


#Question 1. 
```{r}
#read in files 
fed_raw <- readtext::readtext("federalist/*.txt",
                    docvarsfrom = "filenames", 
                    dvsep = "_", 
                    encoding = "ISO-8859-1")
str(fed_raw) #seems to be correct, has 85 texts with doc id and doc var for each
```
```{r}
#turn raw text into corpus 
fp_corpus <- corpus(fed_raw)
class(fp_corpus) #is in fact a corpus now
```


#Question 2. 

```{r}
#tokenize text, remove punctuation, symbols, numbers, and lower case 
fp_corpus_cleaned <- tokens(x=fp_corpus, remove_punct = TRUE,
                         	remove_symbols = TRUE, remove_numbers = TRUE) %>%
                             	tokens_tolower() 
#remove stop words

fp_corpus_cleaned  <- tokens_select(fp_corpus_cleaned, pattern = stopwords('en'),
                                 	selection = 'remove')
#stem the tokens
fp_corpus_cleaned <- tokens_wordstem(fp_corpus_cleaned)
fp_corpus_cleaned

#seems to have worked, no the's, words are chopped up into stems, etc
```

#Question 3.

```{r}
#create DFM 
fed_dfm <- dfm(fp_corpus_cleaned)

fed_dfm
```
```{r}
#top ten words
term_freq <- quanteda.textstats::textstat_frequency(fed_dfm, n = 10)  #would not work without calling the library specifically

# Print the top terms
print(term_freq)
```

#Question 4.and describe what you see. 

```{r}
#word cloud for all documents
textplot_wordcloud(fed_dfm, max_words = 20)

```
 All of these words are relating to governance, power, state and people which
 makes sense as the Federalist Papers are largely seen as a project to convince 
 the American  public of the viability of the Constitution to allow the people 
 to govern a stable nation. These words are all reflective of that purpose, 
 particularly the largest word,and thus most frequent word, state is particularly
 apt. 
```{r}
#word cloud for just Federalist Number 10 
#subset dfm for only Federalist Number 10
fed10_dfm <- fed_dfm["fp10.txt",]
#create wordcloud
textplot_wordcloud(fed10_dfm, max_words = 20)
```
Federalist Paper 10 is one of the few papers that were written by
James Madison. In particular, Federalist 10 is known as one of the most important
and frequently cited Papers and deals prominently with the problem of factions 
and the tyranny of majority rule. This is well represented by these top 20 words
that include small, faction, interest and differ which all reflect Madison's
concern that a majority of individuals could capture the power of the government 
and in a democracy effectively rule a minority. The largest word and thus 
most frequently used word in this document is interest, which aligns with the 
general theme of protecting different people's varying interests against the 
tyranny of the majority. 
#Question 5.

```{r}
topic_model_dfm <- convert(fed_dfm, to = "topicmodels")

## manually set the number of topics to be found to 5
lda_model  <-  LDA(topic_model_dfm, k = 5, method="Gibbs", control = list(seed=808))

## find which features occur most frequently within each topic

mu_fp  <-  tidy(lda_model, matrix = "beta")

## organize the top features

top_fp_features <- mu_fp %>%
	group_by(topic) %>%
	top_n(10,beta) %>% #find top 10 words for each topic
	ungroup() %>%
	arrange(topic,-beta)

## plot the topics

top_fp_features %>%
	mutate(term = reorder_within(term, beta, topic)) %>%
	ggplot(aes(term, beta, fill = factor(topic))) +
	geom_col(show.legend = FALSE) +
	facet_wrap(~ topic, scales = "free") +
	coord_flip() +
	scale_x_reordered()

```
Topic 1 seems to describe the general structure of the American government that 
was outlined in the Constitution and described at length in the Federalist Papers.
We can see specific features of the federalist models of governance including the 
different branches of government (with words such as execut- and senate-) as 
well as other words that align with the various organs of democracy (such as 
"depart-" and "appoint-") which both align with features and processes that 
relate to the functioning of the American Government. 
